---
title: "ASE"
author: "Kin Lau"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    code_folding: hide
    self_contained: yes
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: true
---

```{r keep_figures, cache=TRUE}
# this chunk is just to keep the _files directory even when we turn off cacheing
```

```{r starttime}
# save start time for script
start_tm <- Sys.time()
start_tm
```

```{r make_outdir}
outdir <- "./ASE_submission_out_files/"

dir.create(outdir, recursive=TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=TRUE, message=TRUE, cache=FALSE, cache.lazy = FALSE, dev=c('png','pdf'), fig.width=8, fig.height=8, fig.path=paste0(outdir, "individual_figures/"))

```


# Packages loaded

```{r loadlibs, echo=TRUE, warning=TRUE, message=TRUE, cache=FALSE}
library(dplyr)
library(stringr)
library(readr)
library(SummarizedExperiment)
library(readxl)
library(VariantAnnotation)
library(forcats)
library(scater)
library(ggplot2)
library(patchwork)
library(GenomeInfoDb)
library(ggVennDiagram)
library(GenomicFeatures)
```

# Read in GTF

This is mainly for obtaining the annotations for mito genes. SNPEff already annotated the genes for the linear chromosomes.

```{r read_gtf}
ref_gtf <- "/varidata/research/projects/bbc/versioned_references/2023-10-04_10.07.51_v13/data/dm6_plus_ERCC92/annotation/dm6_plus_ERCC92.gtf"

# To get the gene names, we import using rtracklayer
gene_id2name <- as.data.frame(mcols(import(ref_gtf))) %>% 
  dplyr::select(gene_id, gene_name) %>% unique()
stopifnot(nrow(gene_id2name) == length(unique(gene_id2name$gene_id)))

# to get the GR object for the genes, we read in the GTF as a TxDb
txdb <- makeTxDbFromGFF(ref_gtf)
txdb_genes <- genes(txdb)
txdb_genes_mt <- txdb_genes[seqnames(txdb_genes)=="mitochondrion_genome"]
```


# Read in and filter AD counts

Here, we filter for variants that are biallelic, genic, SNPs, overlapping only one gene and residing on standard chromosomes (not contigs).

```{r get_std_chroms}
ref_fasta <- "/varidata/research/projects/bbc/versioned_references/2023-10-04_10.07.51_v13/data/dm6_plus_ERCC92/sequence/dm6_plus_ERCC92.fa"

# make GenomicRanges from the genome
ref_gr <- as(seqinfo(FaFile(ref_fasta)), "GRanges")

std_chroms_gr <- keepStandardChromosomes(ref_gr, pruning.mode="coarse")
```

```{r read_ad}
vcf_ad <- read_tsv("../unix_analyses/LEMH_scRNA_VBCS-759/w_ERCCs_and_trim/analysis/variant_calling/11a2_extract_ADs/all.merged.filt.PASS.snpeff_inGene.AD.parsed.table")

# keep only the standard chromosomes and mitochondrial genome
std_chrom_var <- vcf_ad$CHROM %in% c(seqlevels(std_chroms_gr), "mitochondrion_genome")
table(std_chrom_var)
vcf_ad <- vcf_ad[std_chrom_var, ]

# When a given variant returns 'ERROR_CHROMOSOME_NOT_FOUND' in SNPEff, it leads to just a '|' in the GENE column. Here we change those to NA to be consistent with the variants with find-able CHROM that are not genic.
vcf_ad$GENE <- ifelse(vcf_ad$GENE=="|", NA, vcf_ad$GENE)

# For variants causing gene fusion, the gene id and gene names will be multiple values separated by '&'
grep(vcf_ad$GENE, pattern = "&", perl = TRUE, value = TRUE)

# split the GENE column into id and name
genes_list <- str_split(vcf_ad$GENE, ",") # split based on comma in case a variant was annotated to multiple genes.
vcf_ad$gene_id <- unlist(lapply(genes_list, function(x) paste(str_extract(x, pattern = "[^\\|]+$"), collapse = ",")))
vcf_ad$gene_name <- unlist(lapply(genes_list, function(x) paste(str_extract(x, pattern = "^[^\\|]+"), collapse = ",")))
```



# Filter the variants

- Keep only those that overlap a gene.
- Keep only those with only one ALT allele (biallelic).
- Keep only SNPs.
- Remove those that overlap more than one gene based on more than one element in GENE column.


```{r var_filters}
# filter for genic variants
genic <- !is.na(vcf_ad$GENE) & !str_detect(vcf_ad$GENE, "^RR\\d+_transposable_element")

# filter for biallelic
biallelic <- !str_detect(vcf_ad$ALT, ",")

# filter for SNPs
snp <- vcf_ad$TYPE == "SNP"

# filter out variants overlapping more than one gene. 
multigene <- str_detect(vcf_ad$GENE, ",")

prop.table(table(genic, biallelic))
prop.table(table(snp, multigene))
prop.table(table(snp, biallelic))
prop.table(table(genic, multigene))

# Do the filtering
vcf_ad <- vcf_ad[which(genic & biallelic & snp & !multigene), ]
nrow(vcf_ad)
stopifnot( all(str_detect(vcf_ad$gene_id, "^FB")) ) # check that there is a valid gene id for all SNPs after filtering for genic SNPs

# how many genes represented after filtering for biallelic , genic, SNPs overlapping only one gene
length(unique(vcf_ad$gene_id))

# check ALT after filtering for biallelic , genic, SNPs overlapping only one gene
stopifnot(all(unique(vcf_ad$ALT) %in% c("T", "A", "G", "C")))
stopifnot(all(unique(vcf_ad$REF) %in% c("T", "A", "G", "C")))

# add rownames
vcf_ad$var_id <- paste(vcf_ad$CHROM, vcf_ad$POS, vcf_ad$REF, vcf_ad$ALT, sep="-")
stopifnot(length(vcf_ad$var_id) == unique(length(vcf_ad$var_id)))
```

Here we prepare the assays and rowData for the SE that we will create.

```{r prep_ad_for_SE}
ad_cols <- sapply(vcf_ad, function(x) all(str_detect(x, "^\\d+(,\\d+)+$"))) # Look for AD columns based on containing values that look like this: 999,999
message("Assuming these are not AD columns: ", paste(colnames(vcf_ad)[!ad_cols], collapse = ", "))
message("Assuming these are AD columns: ", paste(colnames(vcf_ad)[ad_cols], collapse = ", "))

ad_df <- vcf_ad[, ad_cols]

# ensure 1 comma for each data point
stopifnot(all( apply(ad_df, MARGIN = 2, FUN = function(x) all(str_count(x, ",") == 1)) ))

ad_df$var_id <- vcf_ad$var_id

ad_counts <- list(
 ref=ad_df %>% 
   dplyr::mutate(across( one_of(colnames(vcf_ad)[ad_cols]), function(x) as.numeric(str_extract(x, "^[^,]+")) )) %>% 
   tibble::column_to_rownames("var_id") %>%
   as.matrix(),
 alt=ad_df %>% 
   dplyr::mutate(across( one_of(colnames(vcf_ad)[ad_cols]), function(x) as.numeric(str_extract(x, "[^,]+$")) )) %>% 
   tibble::column_to_rownames("var_id") %>%
   as.matrix()
)
ad_counts$total <- ad_counts$ref + ad_counts$alt
ad_counts$ref_ratio <- ad_counts$ref / ad_counts$total

rowdat <- vcf_ad[, !ad_cols] %>% 
  dplyr::mutate(start=POS, end=POS) %>%
  tibble::column_to_rownames("var_id") 

stopifnot( identical( rownames(rowdat), rownames(ad_counts[[1]]) ) )
rowranges <- makeGRangesFromDataFrame(rowdat, keep.extra.columns = TRUE)
```


# Read in DGRP variants, filtered 

Here we read in the VCF file containing genotype calls for the two parents. These have been pre-filtered using bcftools to keep only those that are biallelic, SNPs and with at least one non-ref allele count in either parent.

```{r read_dgrp}
# Reading VCF that was prefiltered using bcftools view --samples line_737,line_352 --max-alleles 2 --types snps --min-ac=1 --trim-alt-alleles
# basically the above filters for just the two parental lines, removes multiallelic variants, keeps only SNPs, and removes variants that were not variant in either line.
# NOTE: I tested the above and it produces the same results as 'bcftools view -O u --samples line_737,line_352 --types snps --trim-alt-alleles --threads 4 dgrp2_dm6.no_chrUn.vcf.gz | bcftools view -o split_filt.vcf --threads 4 --max-alleles 2 --min-ac=1'
dgrp <- readVcf("../unix_analyses/LEMH_scRNA_VBCS-759/w_ERCCs_and_trim/dgrp2_vcf/dgrp2_dm6.no_chrUn.subset.vcf.gz")

# check for non-standard chromosomes
stopifnot( all(seqnames(rowRanges(dgrp)) %in% seqlevels(std_chroms_gr)) )

colnames(dgrp) <- fct_recode(colnames(dgrp), mat.line_737="line_737", pat.line_352="line_352")

GT <- geno(dgrp)$GT
```

Below is the breakdown of genotype calls before additional filtering in R below.

```{r geno_b4_more_filters}
# breakdown of genotypes before additional filtering in R below
prop.table( table(mat.line_737=GT[, "mat.line_737"], pat.line_352=GT[, "pat.line_352"]) )
```

Here we filter for polymorphic sites between the two parents (1/1 in one and 0/0 in the other).

```{r polymorhic_dgrp}
stopifnot(ncol(GT) == 2)
polymorph <- (GT[,1] == "1/1" & GT[,2] == "0/0") | (GT[,1] == "0/0" & GT[,2] == "1/1")
table(polymorph)
dgrp_polymorph <- dgrp[polymorph]
GT_polymorph <- geno(dgrp_polymorph)$GT

# breakdown of homo refs vs homo alts in the polymorphic variants
table(mat.line_737=GT_polymorph[, "mat.line_737"], pat.line_352=GT_polymorph[, "pat.line_352"])
```


```{r prep_dgrp_for_adding_to_SE}
dgrp_gr <- rowRanges(dgrp_polymorph)

stopifnot(all(rownames(GT_polymorph) == names(dgrp_gr)))
mcols(dgrp_gr) <- cbind(mcols(dgrp_gr), as.data.frame(GT_polymorph)) # combine the meta data to the genotype calls

stopifnot(all(dgrp_gr$FILTER=="PASS")) # in DGRP, all the FILTERs appear to be PASS
stopifnot(all(dgrp_gr$QUAL==999)) # in DGRP, all the QUALs appear to be 999
stopifnot(all(is.na(dgrp_gr$paramRangeID))) # not sure where this column comes from, but it's all NAs
mcols(dgrp_gr) <- mcols(dgrp_gr)[, -match( c("FILTER","QUAL","paramRangeID"), colnames(mcols(dgrp_gr)) )]

# add DGRP prefix to columns
colnames(mcols(dgrp_gr)) <- paste0("DGRP.", colnames(mcols(dgrp_gr)))

mcols(dgrp_gr)$DGRP.REF <- as.character(mcols(dgrp_gr)$DGRP.REF)

# Collapse BioStringslist to characterlist, then vector. See https://support.bioconductor.org/p/66874/
clist <- CharacterList(mcols(dgrp_gr)$DGRP.ALT)
stopifnot( all(sapply(clist, length) == 1) )
mcols(dgrp_gr)$DGRP.ALT <- unlist(clist)

```


# Read in meta data for each sample

```{r read_meta_data}
# read barcode decoder
barcode_decoder <- read_tsv("../unix_analyses/LEMH_scRNA_VBCS-759/w_ERCCs_and_trim/whitelists/cellseq192/celseq_barcodes.192.txt",
                            col_names = c("Barcode_index","Barcode"))

# read meta data
meta <- read_excel("../unix_analyses/LEMH_scRNA_VBCS-759/w_ERCCs_and_trim/VBCS-759_meta.xlsx") %>%
  dplyr::rename(Barcode_index="Barcode") %>%
  dplyr::left_join(., barcode_decoder, by="Barcode_index") %>%
  dplyr::mutate(Sample=paste0(Library, ".", Barcode)) %>%
  tibble::column_to_rownames("Sample")

# Add more columns by parsing the ID column
# From Edu: 
# The metadata that is essential is already in the sample name. The first digit is the time of collection. (1, 2, or 3), the second digit is the cohort (A, B and C are all fertilized embryos while only O MEANS unfertilized eggs), the numbers after the hyphen is the replicate (1-40 embryos and 1-8 for unfertilized eggs). For instance, sample 2A-11, is replicate 11 of embryos collected in cohort A after 2 hours while 1O-03 is replicate 03 of unfertilized eggs collected after 1 hour.

stopifnot(all(str_detect(meta$ID, "^[123][ABCO]\\-"))) # check that all values obey the scheme described by Edu
meta <- meta %>%
  dplyr::mutate(time = str_extract(ID, "^[123]"),
                cohort = str_extract(ID, "(?<=^[123])[^\\-]"))

meta <- meta[colnames(ad_counts[[1]]), ]
```


# Make SummarizedExperiment with REF, ALT, total counts etc as assays

```{r make_se}
for(i in 2:length(ad_counts)){
 stopifnot(identical(rownames(ad_counts[[1]]), rownames(ad_counts[[i]]))) 
}
stopifnot( identical(names(rowranges), rownames(ad_counts[[1]])) )

for(i in 2:length(ad_counts)){
 stopifnot(identical(colnames(ad_counts[[1]]), colnames(ad_counts[[i]]))) 
}
stopifnot(identical( colnames(ad_counts[[1]]), rownames(meta) ))

se <- SummarizedExperiment(assays=ad_counts, 
                           rowRanges=rowranges,
                           colData = meta)
```

Here we merge the filtered DGRP (see above) with our variant calls by looking for perfect genomic overlaps (same chrom and position).

```{r add_dgrp_genotype_calls}
# merge DGRP with variant calls by looking for perfect genomic overlaps
overlaps <- findOverlaps(query = dgrp_gr, subject = se, type = "equal")

# ensure no double-matching
stopifnot(sum(duplicated(queryHits(overlaps))) == 0)
stopifnot(sum(duplicated(subjectHits(overlaps))) == 0)

# add the meta data from the DGRP GR to the SE
for(i in 1:ncol(mcols(dgrp_gr))){
  curr_col <- colnames(mcols(dgrp_gr))[i]
  mcols(se)[[ curr_col ]] <- NA
  mcols(se)[[ curr_col ]][subjectHits(overlaps)] <- mcols(dgrp_gr)[[ curr_col ]][queryHits(overlaps)]
}

```

# Rename the sample names to biologically meaningful names

```{r rename_samples}
se$orig_vcf_id <- colnames(se)
colnames(se) <- se$ID
```

# Filter for variants with greater than 5 counts in at least 5 samples for ref and alt, unless it is a mitochondrial variant.

```{r filter_min_counts}
# subset for variant sites with greater than 5 counts in at least 5 samples.
ref_expressed <- rowSums( assay(se, "ref") > 5 ) >= 5
alt_expressed <- rowSums( assay(se, "alt") > 5 ) >= 5
is_mito_gene <- str_detect(names(ref_expressed), "^mito")

# most of the mito variants have only one allele expressed.
table( ref_expressed, alt_expressed, is_mito_gene )

se <- se[(ref_expressed & alt_expressed) | (is_mito_gene & (ref_expressed | alt_expressed))] 

# genes represented
length( unique(rowData(se)$gene_id) )

# count potential fusion genes, which are annotated as geneA&geneB by SNPEff
length( unique(grep(x=rowData(se)$gene_id, pattern="&", value=TRUE)) )

# output sce
write_rds(se, file.path(outdir, "se.rds"))
```


# Compare our variant calling to DGRP

Here we take a look at how many variants had a match in DGRP, and then within those, how many had matching REF and ALT calls.

```{r dgrp_vs_varCalls}
# how many variant calls matched with a DGRP variant
table(ifelse(is.na(mcols(se)$DGRP.REF), "no_match", "matched_by_DGRP"))
matched_se <- se[!is.na(mcols(se)$DGRP.REF)]
stopifnot(all(!is.na(mcols(matched_se)$DGRP.ALT))) # check that DGRP.ALT also has no NA's

# within the matched variants, how many have same REF and ALT basecalls
dgrp_and_varCall_match <- (mcols(matched_se)$REF == mcols(matched_se)$DGRP.REF) & 
  (mcols(matched_se)$ALT == mcols(matched_se)$DGRP.ALT)
table( ifelse(dgrp_and_varCall_match, "Match", "Mismatch" ) )

# subset for variants with the same basecalls for REF and ALT in DGRP and our variant calling
matched_se <- matched_se[dgrp_and_varCall_match]

# Within the variants with matched DGRP variant calls (same REF and ALT). How many genes represented?
length(unique(rowData(matched_se)$gene_id))

# Within the variants with matched DGRP variant calls (same REF and ALT). Variants per gene
summary( as.matrix(table(rowData(matched_se)$gene_id))[, 1] )

```


## Make assays for maternal and paternal alleles instead of REF and ALT

Based on the DGRP parental genotype calls, we make a REF_origin column, which indicates which parent ("mat" or "pat"), the REF allele comes from.

```{r add_REF_origin_column_to_rowData}
mat_is_REF <- rowData(matched_se)$DGRP.mat.line_737=="0/0" & rowData(matched_se)$DGRP.pat.line_352=="1/1"
pat_is_REF <- rowData(matched_se)$DGRP.mat.line_737=="1/1" & rowData(matched_se)$DGRP.pat.line_352=="0/0"
stopifnot( sum(xor(mat_is_REF, pat_is_REF)) == length(matched_se) ) # make sure each gene is either mat_is_REF or pat_is_REF
stopifnot( sum(mat_is_REF, pat_is_REF) == length(matched_se) ) # just double-checking the above

rowData(matched_se)$REF_origin <- ifelse(mat_is_REF, "mat", "pat")

table(rowData(matched_se)$REF_origin)
```

```{r define_get_parental_counts_func}
# 'se' is a SummarizedExperiment with 'ref' and 'alt' assays, and a rowData column named 'REF_origin' that indicates whether a given row's REF allele comes from 'mat' or 'pat'. The 'REF_origin' column is assumed to consist only of 'mat' or 'pat' values, with no NAs.
# A SummarizedExoeriment is returned with a 'mat' and a 'pat' assay.
get_parental_counts <- function(se){
  
  ref_mat <- assay(se, "ref")
  alt_mat <- assay(se, "alt")
  
  for(parent in c("mat", "pat")){
    # set all counts to alt counts
    mat <- alt_mat
    
    # Get vector to indicate which rows correspond to cases where the REF allele belongs to the current 'parent'
    stopifnot( all(rowData(se)$REF_origin %in% c("mat","pat")) )
    ref_is_target_parent <- which(rowData(se)$REF_origin == parent)
    
    # then change the rows where 'ref_is_target_parent' is TRUE to the ref count
    mat[ref_is_target_parent, ] <- ref_mat[ref_is_target_parent, ]
    
    assay(se, parent) <- mat
  }
  
  se
}
```

Here we will fill in the 'mat' and 'pat' assays, by combining specific rows from either the 'ref' or the 'alt' assays based on the value of the 'REF_origin' column.

```{r add_mat_and_pat_assays}
matched_se <- get_parental_counts(matched_se)

```


```{r define_var_rank_function}
add_variant_ranks_to_SCE <- function(sce){
  rowdat <- as.data.frame( rowData(sce), optional = TRUE ) %>% 
    tibble::rownames_to_column("var_id")
  
  # Calculate metrics for ranking variants below
  rowdat$tot_counts <- rowSums( assay(sce, "total") )
  rowdat$num_samps_expr_both_alleles <- rowSums( (assay(sce, "ref") > 0) & (assay(sce, "alt") > 0) )
  
  # add rankings for variants per gene
  rowdat <- rowdat %>%
    dplyr::mutate(orig_row_order=row_number()) %>%
    dplyr::group_by(gene_id) %>%
    dplyr::arrange(desc(num_samps_expr_both_alleles), desc(tot_counts)) %>%
    dplyr::mutate(var_rank=row_number()) %>%
    dplyr::ungroup()
  
  # fix the row order
  rowdat <- rowdat %>%
    dplyr::arrange(orig_row_order) %>%
    dplyr::select(-orig_row_order) %>%
    tibble::column_to_rownames("var_id") 
  
  rowdat <- DataFrame(rowdat)
  
  stopifnot( identical(rownames(sce), rownames(rowdat)) )
  rowData(sce) <- rowdat
  
  sce
}

```

The last modification to the SCE/SE object is to add a 'var_rank' column in the rowData to indicate the ranking of the variants of a given gene.

```{r add_ranks_to_matched_sce}
matched_sce <- as(matched_se, "SingleCellExperiment")
matched_sce <- add_variant_ranks_to_SCE(matched_sce)
```

Output both RDS and tsv files for the different assays.

```{r out_matched}
# output sce
write_rds(matched_sce, file.path(outdir, "matched_sce.rds"))

for ( assay_nm in assayNames(matched_sce) ){
  outdf <- as.data.frame( cbind(rowData(matched_sce), assay(matched_sce, assay_nm)), optional=TRUE )
  write_tsv( outdf, file.path(outdir, paste0("matched.", assay_nm, ".tsv.gz")) )
}
```

## Look at allele counts by cohort

```{r define_mat_and_pat_qc_func}
make_mat_and_pat_qc_plots <- function(sce){
  sce.mat <- addPerCellQC(sce, assay.type="mat")
  sce.pat <- addPerCellQC(sce, assay.type="pat")
  
  plot_p1 <- function(x, title) plotColData(x, x = "cohort", y="sum", colour_by="time", other_fields="cohort") + ggtitle(title) + scale_y_log10()
  p1 <- ( plot_p1(sce.mat, "Mat counts") ) / ( plot_p1(sce.pat, "Pat counts") ) + 
    patchwork::plot_annotation(title="Sum counts across variant sites")
  
  plot_p2 <- function(x, title) plotColData(x, x = "cohort", y="detected", colour_by="time", other_fields="cohort") + ggtitle(title) + scale_y_log10()
  p2 <- ( plot_p2(sce.mat, "Mat counts") ) / ( plot_p2(sce.pat, "Pat counts") ) + 
    patchwork::plot_annotation(title="Variant sites detected")
  
  # Relationship between sum and detected
  plot_p3 <- function(x, title) plotColData(x, x = "sum", y="detected", colour_by="time", other_fields="cohort") + 
            facet_wrap(~cohort, nrow = 1) + ggtitle(title)
  p3 <- ( plot_p3(sce.mat, "Mat counts") ) / ( plot_p3(sce.pat, "Pat counts") )
  
  list(p1, p2, p3)
}

```

Here we filter the data for only the 1-ranked variants (so that we have 1 variant per gene) and plot some summary statistics based on total counts and total genes detected using the 'mat' and 'pat' counts.

```{r counts_by_cohort, fig.height=5, fig.width=8}
matched_sce.1_var_per_gene <- matched_sce[ rowData(matched_sce)$var_rank == 1, ]
nrow(matched_sce.1_var_per_gene)
stopifnot(nrow(matched_sce.1_var_per_gene) == length(unique(rowData(matched_sce)$gene_id)))

make_mat_and_pat_qc_plots(matched_sce.1_var_per_gene)
```

## Ref to total counts ratio

If there is no biased ASE, we expect the ref ratio to be 0.5 but mapping bias of the reference allele compared to the alternate allele could nudge this higher than 0.5. Here, we find the median ref ratio across groups defined by time and cohort, then plot violin plots. Groups 3 A, B and C show a median at about 0.5. The other groups (earlier time points and the unfertilized cohort O) all show bimodal distributions peaking at 0 or 1. This makes sense somewhat considering that the paternal allele takes some time to ramp up and in the O cohort, there should be no expression of the paternal allele.

```{r ref_ratio_dist, fig.height=4}
ref_ratio_agg <- aggregateAcrossCells(matched_sce.1_var_per_gene, 
                                      ids=colData(matched_sce.1_var_per_gene)[, c("time", "cohort")],
                                      use.assay.type="ref_ratio",
                                      statistics="median")
colnames(ref_ratio_agg) <- paste0(ref_ratio_agg$time, ".", ref_ratio_agg$cohort)

ref_ratio_agg_mat <- assay(ref_ratio_agg, "ref_ratio")
ref_ratio_agg_df <- as.data.frame(ref_ratio_agg_mat) %>%
  tidyr::pivot_longer(cols=everything(), names_to="group", values_to = "median_ref_ratio")

ref_ratio_agg_df <- na.omit(ref_ratio_agg_df)
num_vars_per_group <- dplyr::count(ref_ratio_agg_df, group)

ggplot(na.omit(ref_ratio_agg_df), aes(x=group, y=median_ref_ratio)) + 
  geom_violin(draw_quantiles=c(0.5)) +
  geom_text(data = num_vars_per_group, aes(y = 1, label = n),  nudge_y=0.05) +
  ggtitle("Distribution of median ref ratio by group (# sites in each plot indicated)")
```


# SessionInfo

```{r sessioninfo}
sessionInfo()
```

# Time

```{r endtime}
# output time taken to run script
end_tm <- Sys.time()
end_tm
end_tm - start_tm

```
